Improved association in a classical density functional theory for water

### 2013-09-06 papers/water-saft/paper.tex
Abstract changes to water paper Tested on node33. Took 0:22.52.

\documentclass[twocolumn,amsmath,amssymb,prl]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\begin{abstract}
We develop an improved version of our old functional.
\end{abstract}
\maketitle

>>>>

\documentclass[preprint, endfloats,amsmath,amssymb,jcp]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\begin{abstract}
We present a modification to our recently published SAFT-based classical
density functional theory for water.
%
We have recently developed and tested a functional for the averaged
radial distribution function at contact of the hard-sphere fluid
that is dramatically more accurate at interfaces than earlier
approximations.
%
We now incorporate this improved functional into the association term
of our free energy functional for water, improving its description of
hydrogen bonding.
%
We examine the effect of this improvement by studying two hard solutes: a
hard hydrophobic rod and a hard sphere.
%
The improved functional leads to a moderate change in the density
profile and a large decrease in the number of hydrogen bonds broken in
the vicinity of the solutes.
\end{abstract}
\maketitle
